\makeatletter
\ifthenelse{\pdf@strcmp{\languagename}{english}=0}
{\addcontentsline{toc}{chapter}{Acknowledgments}}
{\addcontentsline{toc}{chapter}{Danksagungen}}
\makeatother
\thispagestyle{empty}

\vspace*{20mm}

\begin{center}
\makeatletter
\ifthenelse{\pdf@strcmp{\languagename}{english}=0}
{\usekomafont{section} Acknowledgments}
{\usekomafont{section} Danksagungen}
\makeatother
\end{center}

\vspace{10mm}

Without doubt the very first name here is my father Musa Kazım Uzdoğan, who lost his fight to COVID-19 at the very beginning of this thesis. He with my mother Ayşegül Uzdoğan have been my biggest supporters throughout my life and put everything they had for me to become successful. Definitely, I am standing on the shoulders of giants. I know you would be extremely proud to see me achieve this. We will be loving and remembering you forever. I am also thankful for having a larger family who always showed their love and support through the difficult times.

Secondly, big thanks to my advisor Benjamin Sturm for his guidance and great communication throughout this work. I really enjoyed our discussions and appreciate your extensive feedback each time we met, although always virtually. I would also like to thank Prof. Ali Sunyaev and Prof. Jens Großklags for providing me the opportunity to work on this topic, and Tibor Posa for his reviews. Another mention goes to my colleagues at Max Planck Digital Library where I was working on the project bloxberg. Particularly to James Lawton, who introduced me to this problem and whom I enjoyed closely working with a lot. Also, I want to thank all interviewees for taking their time and providing valuable insights: João Pedro Oliveira, Tiago Paixão, Kevin Wittek, and two pseudonymous interviewees.

Finally, even though we never met, I want to commemorate Jon Tennant here, a great communicator and a tireless proponent of open science whose loss shocked many. I benefited and influenced by his works to a great extent, and the legacy he left helped me shape this work a lot. 

\cleardoublepage{}
